EXAM Fits and Predictions

### 2023-11-13 Manuscript/htw_exam.qmd
model tables

---
title: EXAM Fits and Predictions
date: last-modified
categories: [Simulation, ALM, EXAM, R]
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: true
---

@@

alm_plot()

@@

For the hybrid model, predictions are computed by first generating separate predictions from ALM and EXAM, and then combining them using the following equation: $\hat{y} = (1 - w) \cdot alm_pred + w \cdot exam_pred$. For the grid search, the weight parameter is varied from 0 to 1, and the resulting RMSE is recorded.

@@

@@

almParamsV <- cbind(Model="ALM Test Only",pluck(a_te_v, "Fit"), pluck(a_te_v, "test") %>% summarise(Test_RMSE=RMSE(y,pred)) ) |>
  rbind(cbind(Model="ALM Test & Train", pluck(a_tetr_v,"Fit"), pluck(a_tetr_v, "test") %>% summarise(Test_RMSE=RMSE(y,pred)))) |>
  rbind(cbind(Model="ALM Train Only", pluck(a_tr_v, "Fit"), pluck(a_tr_v, "test") %>% summarise(Test_RMSE=RMSE(y,pred)))) |>
  mutate(across(where(is.numeric), \(x) round(x, 3)))

examParamsV <- cbind(Model="EXAM Test Only",pluck(ex_te_v, "Fit"), pluck(ex_te_v, "test") %>% summarise(Test_RMSE=RMSE(y,pred))) |>
  rbind(cbind(Model="EXAM Test & Train", pluck(ex_tetr_v,"Fit"), pluck(ex_tetr_v, "test") %>% summarise(Test_RMSE=RMSE(y,pred)))) |>
  rbind(cbind(Model="EXAM Train Only", pluck(ex_tr_v, "Fit"), pluck(ex_tr_v, "test") %>% summarise(Test_RMSE=RMSE(y,pred)))) |>
  mutate(across(where(is.numeric), \(x) round(x, 3)))

hybridParamsV <-cbind(Model="Hybrid Test Only",pluck(hybrid_te_v, "Fit"), pluck(hybrid_te_v, "test") %>% summarise(Test_RMSE=RMSE(y,pred))) |>
  rbind(cbind(Model="Hybrid Test & Train", pluck(hybrid_tetr_v,"Fit"), pluck(hybrid_tetr_v, "test") %>% summarise(Test_RMSE=RMSE(y,pred)))) |>
  rbind(cbind(Model="Hybrid Train Only", pluck(hybrid_tr_v, "Fit"), pluck(hybrid_tr_v, "test") %>% summarise(Test_RMSE=RMSE(y,pred)))) |>
  mutate(across(where(is.numeric), \(x) round(x, 3)))

almParamsC <- cbind(Model="ALM Test Only",pluck(a_te_c, "Fit"), pluck(a_te_c, "test") %>% summarise(Test_RMSE=RMSE(y,pred)) ) |>
  rbind(cbind(Model="ALM Test & Train", pluck(a_tetr_c,"Fit"), pluck(a_tetr_c, "test") %>% summarise(Test_RMSE=RMSE(y,pred)))) |>
  rbind(cbind(Model="ALM Train Only", pluck(a_tr_c, "Fit"), pluck(a_tr_c, "test") %>% summarise(Test_RMSE=RMSE(y,pred)))) |>
  mutate(across(where(is.numeric), \(x) round(x, 3)))

examParamsC <- cbind(Model="EXAM Test Only",pluck(ex0_te_c, "Fit"), pluck(ex0_te_c, "test") %>% summarise(Test_RMSE=RMSE(y,pred))) |>
  rbind(cbind(Model="EXAM Test & Train", pluck(ex0_tetr_c,"Fit"), pluck(ex0_tetr_c, "test") %>% summarise(Test_RMSE=RMSE(y,pred)))) |>
  rbind(cbind(Model="EXAM Train Only", pluck(ex0_tr_c, "Fit"), pluck(ex0_tr_c, "test") %>% summarise(Test_RMSE=RMSE(y,pred)))) |>
  mutate(across(where(is.numeric), \(x) round(x, 3)))

hybridParamsC <-cbind(Model="Hybrid Test Only",pluck(hybrid_te_c, "Fit"), pluck(hybrid_te_c, "test") %>% summarise(Test_RMSE=RMSE(y,pred))) |>
  rbind(cbind(Model="Hybrid Test & Train", pluck(hybrid_tetr_c,"Fit"), pluck(hybrid_tetr_c, "test") %>% summarise(Test_RMSE=RMSE(y,pred)))) |>
  rbind(cbind(Model="Hybrid Train Only", pluck(hybrid_tr_c, "Fit"), pluck(hybrid_tr_c, "test") %>% summarise(Test_RMSE=RMSE(y,pred)))) |>
  mutate(across(where(is.numeric), \(x) round(x, 3)))

@@

```{r}
#| label: tbl-e1-model-fits2V
#| tbl-cap: Varied Group - Fit Parameters and Model RMSE

@@

```{r}
#| label: tbl-e1-model-fitsC
#| tbl-cap: Constant Group - Fit Parameters and Model RMSE

pander(almParamsC, caption="ALM"); pander(examParamsC, caption="EXAM"); pander(hybridParamsC,caption="Hybrid")
```

@@

vte <-  pluck(a_te_v, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex_te_v, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_te_v, "test") |> pull(pred)) |>  
  pivot_longer(Observed:Hybrid, names_to="Model", values_to = "vx") |> 
  ggplot(aes(x,vx,fill=Model, group=Model)) +geom_bar(position="dodge",stat="identity") +
  scale_fill_manual(values=col_themes$wes2)+
  scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(ds$x)))+ylim(0,1500) +
  theme(legend.title = element_blank(), legend.position="top") +ggtitle("Fit to Test Only")

vtetr <-  pluck(a_tetr_v, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex_tetr_v, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_tetr_v, "test") |> pull(pred)) |>  
  pivot_longer(Observed:Hybrid, names_to="Model", values_to = "vx") |> 
  ggplot(aes(x,vx,fill=Model, group=Model)) +geom_bar(position="dodge",stat="identity") + 
  scale_fill_manual(values=col_themes$wes2)+
  scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(ds$x)))+ylim(0,1500) +
  theme(legend.title = element_blank(), legend.position="top") +ggtitle("Fit to Test and Train")

vtr <-  pluck(a_tr_v, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex_tr_v, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_tr_v, "test") |> pull(pred)) |>  
  pivot_longer(Observed:Hybrid, names_to="Model", values_to = "vx") |> 
  ggplot(aes(x,vx,fill=Model, group=Model)) +geom_bar(position="dodge",stat="identity") +
  scale_fill_manual(values=col_themes$wes2)+
  scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(ds$x)))+ylim(0,1500) +
  theme(legend.title = element_blank(), legend.position="top") +ggtitle("Fit to Train Only")

vte/vtetr/vtr

@@

## Varied Testing
```{r fig.height=11, fig.width=11}
#| label: tbl-e1-predsV
#| tbl-cap: Varied group - mean model predictions vs. observations
#| 
tvte<- pluck(a_te_v, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex_te_v, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_te_v, "test") |> pull(pred))

tvtetr<-pluck(a_tetr_v, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex_tetr_v, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_tetr_v, "test") |> pull(pred))

tvtr<- pluck(a_tr_v, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex_tr_v, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_tr_v, "test") |> pull(pred))

pander(tvte, caption="Varied fit to test only")
pander(tvtetr,caption="Varied fit to train and test")
pander(tvtr,caption="Varied fit to train only")

@@

cte <-  pluck(a_te_c, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex0_te_c, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_te_c, "test") |> pull(pred)) |>  
  pivot_longer(Observed:Hybrid, names_to="Model", values_to = "vx") |> 
  ggplot(aes(x,vx,fill=Model, group=Model)) +geom_bar(position="dodge",stat="identity") +
  scale_fill_manual(values=col_themes$wes2)+
  scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(ds$x)))+ylim(0,1500) +
  theme(legend.title = element_blank(), legend.position="top") +ggtitle("Fit to Test Only")

ctetr <-  pluck(a_tetr_c, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex0_tetr_c, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_tetr_c, "test") |> pull(pred)) |>  
  pivot_longer(Observed:Hybrid, names_to="Model", values_to = "vx") |> 
  ggplot(aes(x,vx,fill=Model, group=Model)) +geom_bar(position="dodge",stat="identity") + 
  scale_fill_manual(values=col_themes$wes2)+
  scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(ds$x)))+ylim(0,1500) +
  theme(legend.title = element_blank(), legend.position="top") +ggtitle("Fit to Test and Train")

ctr <-  pluck(a_tr_c, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex0_tr_c, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_tr_c, "test") |> pull(pred)) |>  
  pivot_longer(Observed:Hybrid, names_to="Model", values_to = "vx") |> 
  ggplot(aes(x,vx,fill=Model, group=Model)) +geom_bar(position="dodge",stat="identity") +
  scale_fill_manual(values=col_themes$wes2)+
  scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(ds$x)))+ylim(0,1500) +
  theme(legend.title = element_blank(), legend.position="top") +ggtitle("Fit to Train Only")

cte/ctetr/ctr

@@

```{r}
#| label: tbl-e1-predsC
#| tbl-cap: Constant group - mean model predictions vs. observations
#| 
tcte<- pluck(a_te_c, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex0_te_c, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_te_c, "test") |> pull(pred))

tctetr<-pluck(a_tetr_c, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex0_tetr_c, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_tetr_c, "test") |> pull(pred))

tctr<- pluck(a_tr_c, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex0_tr_c, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_tr_c, "test") |> pull(pred))

pander(tcte, caption="Constant fit to test only")
pander(tctetr,caption="Constant fit to train and test")
pander(tctr,caption="Constant fit to train only")

>>>>

---
title: EXAM Fits and Predictions
date: last-modified
categories: [Simulation, ALM, EXAM, R]
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: true
  echo: false
---

@@

#alm_plot()

@@

For the hybrid model, predictions are computed by first generating separate predictions from ALM and EXAM, and then combining them using the following equation: $\hat{y} = (1 - w) \cdot alm_pred + w \cdot exam-pred$. For the grid search, the weight parameter is varied from 0 to 1, and the resulting RMSE is recorded.

@@

```{r}
#| eval: false
#| 
extract_params <- function(model_name, model_data) {
  cbind(Model = model_name,
        pluck(model_data, "Fit"),
        pluck(model_data, "test") %>% summarise(Test_RMSE = RMSE(y, pred))
       ) %>%
  mutate(across(where(is.numeric), \(x) round(x, 3)))
}

# Define model names and data
model_names <- c("ALM Test Only", "ALM Test & Train", "ALM Train Only", "EXAM Test Only", "EXAM Test & Train", "EXAM Train Only", "Hybrid Test Only", "Hybrid Test & Train", "Hybrid Train Only")
model_data_v <- list(a_te_v, a_tetr_v, a_tr_v, ex_te_v, ex_tetr_v, ex_tr_v, hybrid_te_v, hybrid_tetr_v, hybrid_tr_v)
model_data_c <- list(a_te_c, a_tetr_c, a_tr_c, ex0_te_c, ex0_tetr_c, ex0_tr_c, hybrid_te_c, hybrid_tetr_c, hybrid_tr_c)

params_list_v <- Map(extract_params, model_names, model_data_v)
params_list_c <- Map(extract_params, model_names, model_data_c)

almParamsV <- do.call(rbind, params_list_v[1:3])
examParamsV <- do.call(rbind, params_list_v[4:6])
hybridParamsV <- do.call(rbind, params_list_v[7:9])

almParamsC <- do.call(rbind, params_list_c[1:3])
examParamsC <- do.call(rbind, params_list_c[4:6])
hybridParamsC <- do.call(rbind, params_list_c[7:9])

```{r}
#| label: tbl-e1-cogmodel
#| tbl-cap: Fit Parameters and Model RMSE
#| column: screen-inset-right
#|

create_combined_df <- function(model_names, model_data, group) {
  do.call(rbind, Map(function(name, data) {
    model<- ifelse(grepl("Hybrid", name), "Hybrid", ifelse(grepl("EXAM", name), "EXAM", "ALM"))
    fit_method <- gsub(".*(Test Only|Test & Train|Train Only).*", "\\1", name)
    extract_params(model, data, group, fit_method)
  }, model_names, model_data))
}

# Adjust the extract_params function to accept and include the fit_method parameter
extract_params <- function(model_name, model_data, group, fit_method) {
  params_df <- cbind(Model = model_name, Group = group, Fit_Method = fit_method,
                     pluck(model_data, "Fit"), pluck(model_data, "test") %>% summarise(Test_RMSE = round(RMSE(y, pred)),1)) %>% 
                     mutate(across(where(is.numeric), round, 4))
  if (!"w" %in% names(params_df)) {
    params_df$w <- NA
  }
  return(params_df)
}

model_classes <- c("ALM", "EXAM", "Hybrid")
groups <- c("V", "C")

model_names_v <- c("ALM Test Only", "ALM Test & Train", "ALM Train Only", "EXAM Test Only", "EXAM Test & Train", "EXAM Train Only", "Hybrid Test Only", "Hybrid Test & Train", "Hybrid Train Only")

#model_names_v <- c("Test Only", "Test & Train", "Train Only")
model_names_c <- model_names_v

model_data_v <- list(a_te_v, a_tetr_v, a_tr_v, ex_te_v, ex_tetr_v, ex_tr_v, hybrid_te_v, hybrid_tetr_v, hybrid_tr_v)
model_data_c <- list(a_te_c, a_tetr_c, a_tr_c, ex0_te_c, ex0_tetr_c, ex0_tr_c, hybrid_te_c, hybrid_tetr_c, hybrid_tr_c)

combined_params_v <- create_combined_df(model_names_v, model_data_v, "Varied")
combined_params_c <- create_combined_df(model_names_c, model_data_c, "Constant")

all_combined_params <- rbind(combined_params_v, combined_params_c)

library(flextable)

identity <- function (x){x}
fmt_iden <- function(x, digits = 2) {
  paste0(x)
}

# all_combined_params %>% 
#   group_by(Group, Model) |> summarise(across(c(c,lr,Test_RMSE), ~max(.x,na.rm=TRUE)))

grouped_params <- all_combined_params %>% 
  group_by(Group, Model) %>%
  summarise(across(c(c, lr, w, Value, Test_RMSE), ~identity(.x))) %>%
  ungroup()

ft <- flextable(all_combined_params) %>% 
  theme_vanilla() %>% 
  align(align = "left", part = "all") %>% 
  colformat_double(digits = 2) %>% 
  autofit()

# Pre-calculate the averages and standard deviations
all_combined_params2 <- all_combined_params %>%
  group_by(Fit_Method, Group, Model) %>%
  summarise(
    c_stats = fmt_iden(c),
    lr_stats = fmt_iden(lr),
     rmse_stats = fmt_iden(Test_RMSE),
    .groups = "drop"
  )

# Use the pre-calculated stats in tabulator
tab <- tabulator(
  x = all_combined_params2, rows = c("Fit_Method", "Model"),
  columns = "Group",
  `c` = as_paragraph(c_stats),
  `lr` = as_paragraph(lr_stats),
  `Test_RMSE` = as_paragraph(rmse_stats)
) %>%
  as_flextable() |> align(align="left",part="all")

tab

# a=aggregate(c ~ Group+Model+Fit_Method, data=all_combined_params,identity)
# 
# all_combined_params |> group_by(Model, Group,Fit_Method) %>% 
#   summarise(
#     across(
#       all_of(c("c", "lr")),
#       list(
#         c = ~ identity(.x),
#         lr = ~ identity(.x)
#       )
#     )
#   ) %>% flextable() %>% separate_header()
# 
# 
# ft_1 <-  tabulator(
#   x = all_combined_params,
#   rows = "Group",
#   columns = c("Fit_Method","Model"),
#   `c1` = c,
#   `$lr$` = as_paragraph(lr) ) %>% as_flextable()
# 
# ft_1
```

@@

tab

@@

```{r}
#| label: tbl-e1-model-fits2V
#| tbl-cap: Varied Group - Fit Parameters and Model RMSE
#| eval: false

@@

```{r}
#| label: tbl-e1-model-fitsC
#| tbl-cap: Constant Group - Fit Parameters and Model RMSE
#| eval: false
#| 
pander(almParamsC, caption="ALM"); pander(examParamsC, caption="EXAM"); pander(hybridParamsC,caption="Hybrid")
```

@@

# vte <-  pluck(a_te_v, "test") |> rename(ALM=pred,Observed=y) %>% 
#   cbind(.,EXAM=pluck(ex_te_v, "test") |> pull(pred)) %>%
#   cbind(., Hybrid=pluck(hybrid_te_v, "test") |> pull(pred)) |>  
#   pivot_longer(Observed:Hybrid, names_to="Model", values_to = "vx") |> 
#   ggplot(aes(x,vx,fill=Model, group=Model)) +geom_bar(position="dodge",stat="identity") +
#   scale_fill_manual(values=col_themes$wes2)+
#   scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(ds$x)))+ylim(0,1500) +
#   theme(legend.title = element_blank(), legend.position="top") +ggtitle("Fit to Test Only")

# vtetr <-  pluck(a_tetr_v, "test") |> rename(ALM=pred,Observed=y) %>% 
#   cbind(.,EXAM=pluck(ex_tetr_v, "test") |> pull(pred)) %>%
#   cbind(., Hybrid=pluck(hybrid_tetr_v, "test") |> pull(pred)) |>  
#   pivot_longer(Observed:Hybrid, names_to="Model", values_to = "vx") |> 
#   ggplot(aes(x,vx,fill=Model, group=Model)) +geom_bar(position="dodge",stat="identity") + 
#   scale_fill_manual(values=col_themes$wes2)+
#   scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(ds$x)))+ylim(0,1500) +
#   theme(legend.title = element_blank(), legend.position="top") +ggtitle("Fit to Test and Train")

# vtr <-  pluck(a_tr_v, "test") |> rename(ALM=pred,Observed=y) %>% 
#   cbind(.,EXAM=pluck(ex_tr_v, "test") |> pull(pred)) %>%
#   cbind(., Hybrid=pluck(hybrid_tr_v, "test") |> pull(pred)) |>  
#   pivot_longer(Observed:Hybrid, names_to="Model", values_to = "vx") |> 
#   ggplot(aes(x,vx,fill=Model, group=Model)) +geom_bar(position="dodge",stat="identity") +
#   scale_fill_manual(values=col_themes$wes2)+
#   scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(ds$x)))+ylim(0,1500) +
#   theme(legend.title = element_blank(), legend.position="top") +ggtitle("Fit to Train Only")

# vte/vtetr/vtr

@@

## Varied Testing
```{r fig.height=11, fig.width=11}
#| label: tbl-e1-predsV
#| tbl-cap: Varied group - mean model predictions vs. observations
#| 
# tvte<- pluck(a_te_v, "test") |> rename(ALM=pred,Observed=y) %>% 
#   cbind(.,EXAM=pluck(ex_te_v, "test") |> pull(pred)) %>%
#   cbind(., Hybrid=pluck(hybrid_te_v, "test") |> pull(pred))

# tvtetr<-pluck(a_tetr_v, "test") |> rename(ALM=pred,Observed=y) %>% 
#   cbind(.,EXAM=pluck(ex_tetr_v, "test") |> pull(pred)) %>%
#   cbind(., Hybrid=pluck(hybrid_tetr_v, "test") |> pull(pred))

# tvtr<- pluck(a_tr_v, "test") |> rename(ALM=pred,Observed=y) %>% 
#   cbind(.,EXAM=pluck(ex_tr_v, "test") |> pull(pred)) %>%
#   cbind(., Hybrid=pluck(hybrid_tr_v, "test") |> pull(pred))

# pander(tvte, caption="Varied fit to test only")
# pander(tvtetr,caption="Varied fit to train and test")
# pander(tvtr,caption="Varied fit to train only")

@@

# cte <-  pluck(a_te_c, "test") |> rename(ALM=pred,Observed=y) %>% 
#   cbind(.,EXAM=pluck(ex0_te_c, "test") |> pull(pred)) %>%
#   cbind(., Hybrid=pluck(hybrid_te_c, "test") |> pull(pred)) |>  
#   pivot_longer(Observed:Hybrid, names_to="Model", values_to = "vx") |> 
#   ggplot(aes(x,vx,fill=Model, group=Model)) +geom_bar(position="dodge",stat="identity") +
#   scale_fill_manual(values=col_themes$wes2)+
#   scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(ds$x)))+ylim(0,1500) +
#   theme(legend.title = element_blank(), legend.position="top") +ggtitle("Fit to Test Only")

# ctetr <-  pluck(a_tetr_c, "test") |> rename(ALM=pred,Observed=y) %>% 
#   cbind(.,EXAM=pluck(ex0_tetr_c, "test") |> pull(pred)) %>%
#   cbind(., Hybrid=pluck(hybrid_tetr_c, "test") |> pull(pred)) |>  
#   pivot_longer(Observed:Hybrid, names_to="Model", values_to = "vx") |> 
#   ggplot(aes(x,vx,fill=Model, group=Model)) +geom_bar(position="dodge",stat="identity") + 
#   scale_fill_manual(values=col_themes$wes2)+
#   scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(ds$x)))+ylim(0,1500) +
#   theme(legend.title = element_blank(), legend.position="top") +ggtitle("Fit to Test and Train")

# ctr <-  pluck(a_tr_c, "test") |> rename(ALM=pred,Observed=y) %>% 
#   cbind(.,EXAM=pluck(ex0_tr_c, "test") |> pull(pred)) %>%
#   cbind(., Hybrid=pluck(hybrid_tr_c, "test") |> pull(pred)) |>  
#   pivot_longer(Observed:Hybrid, names_to="Model", values_to = "vx") |> 
#   ggplot(aes(x,vx,fill=Model, group=Model)) +geom_bar(position="dodge",stat="identity") +
#   scale_fill_manual(values=col_themes$wes2)+
#   scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(ds$x)))+ylim(0,1500) +
#   theme(legend.title = element_blank(), legend.position="top") +ggtitle("Fit to Train Only")

# cte/ctetr/ctr

@@

```{r}
#| label: tbl-e1-predsC
#| tbl-cap: Constant group - mean model predictions vs. observations
#| 
# tcte<- pluck(a_te_c, "test") |> rename(ALM=pred,Observed=y) %>% 
#   cbind(.,EXAM=pluck(ex0_te_c, "test") |> pull(pred)) %>%
#   cbind(., Hybrid=pluck(hybrid_te_c, "test") |> pull(pred))

# tctetr<-pluck(a_tetr_c, "test") |> rename(ALM=pred,Observed=y) %>% 
#   cbind(.,EXAM=pluck(ex0_tetr_c, "test") |> pull(pred)) %>%
#   cbind(., Hybrid=pluck(hybrid_tetr_c, "test") |> pull(pred))

# tctr<- pluck(a_tr_c, "test") |> rename(ALM=pred,Observed=y) %>% 
#   cbind(.,EXAM=pluck(ex0_tr_c, "test") |> pull(pred)) %>%
#   cbind(., Hybrid=pluck(hybrid_tr_c, "test") |> pull(pred))

# pander(tcte, caption="Constant fit to test only")
# pander(tctetr,caption="Constant fit to train and test")
# pander(tctr,caption="Constant fit to train only")
